---
title: "Reading Data from the Web"
author: "Wenxin Tian"
date: "`r Sys.Date()`"
output: github_document
---

Website = HTML + CSS

HTML controls content, and CSS controls appearance. So extracting information comes down to choosing the unique selector tag.

Workflow:

- Download HTML using `read_html()`
- Extract elements using `html_elements()` and CSS selector
- Extract data with `html_extract()` and `html_table()`

Load libraries:

```{r}
library(tidyverse)
library(rvest)
library(httr)
```

## Read Tables from HTML:

```{r, eval = F}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(url)

# Imports every table stored as a list:

nsduh_html |>
  html_table()

# Use specific ones:

marj_use_df =
  nsduh_html |>
  html_table() |>
  first() |>
  slice(-1)  # removes first row

marj_use_df
```

## Selector Gadget:

Import Star Wars data, which are not tables:

```{r}
starwars_url = "https://www.imdb.com/list/ls070150896/"

starwars_html = read_html(starwars_url)
```

Use Selector Gadget to select css tags on the website and paste it below:
```{r}
starwars_html |>
  html_elements(".lister-item-header a")

starwars_html |>
  html_elements(".lister-item-header a") |>
  html_text()

starwars_html |>
  html_elements(".text-small:nth-child(7) span:nth-child(5)") |>
  html_text()
```

Make a df:

```{r}
startwars_df =
  tibble(
    title = 
      starwars_html |>
      html_elements(".lister-item-header a") |>
      html_text(),
    gross_rev = 
      starwars_html |>
      html_elements(".text-small:nth-child(7) span:nth-child(5)") |>
      html_text()
  )
```

## APIs:

NYC Water Dataset:

```{r}
nyc_water = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.csv") |> 
  content()
```

BRFSS Dataset:

```{r}
# By defalt, GET will download only first 1000 lines.
brfss_smart2010 = 
  GET("https://chronicdata.cdc.gov/resource/acme-vg9e.csv") |>
  content("parsed")

# To download more lines:
brfss_smart2010 = 
  GET("https://chronicdata.cdc.gov/resource/acme-vg9e.csv",
      query = list("$limit" = 5000)) |>
  content("parsed")
```

More complicated example:

```{r}
poke_df = 
  GET("http://pokeapi.co/api/v2/pokemon/1") |>
  content()

poke_df$name
```





